%-------------------------
% Resume in Latex
% Author : Umut Uz
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{#2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Umut Uz} & Email : \href{mailto:umutuz7@gmail.com}{umutuz7@gmail.com}\\
		& Mobile : +90-531-918-54-92 \\
		& Linkedin: \href{https://www.linkedin.com/in/umutuz/}{/in/umutuz}\\
		& Medium: \href{https://medium.com/@umutuz7}{@umutuz7}\\
		& Github: \href{https://github.com/umutuz7}{umutuz7}\\
	\end{tabular*}
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Bilyoner}{Istanbul}
	{Senior Android Engineer}{Apr 2018 - Present}
	\resumeItemListStart
	\resumeItem{New Generation: }
	{Bilyoner is the largest betting company in Turkey with more than \textbf{1 million monthly active users}. Written completely in \textbf{Kotlin}, the project benefits \textbf{clean architecture} pattern with 4 separate modules for separation of concerns. \textbf{RxJava2, Dagger2, Retrofit, Mockito, JUnit, Espresso} are the main libraries used extensively throughout the application. \textbf{MVP} pattern is used to organize the UI module.}
	\resumeItem{Legacy Application: }
	{The app was taken over from an outsourced company. Crash free sessions increased from \%91 to \%99.9 after making a deep analysis of the 9 year-old application and fixing all major/minor bugs.}
	\resumeItemListEnd
	
	\resumeSubheading
	{EMBonds}{Istanbul (comp. based in London)}
	{Software Engineer}{Jul 2017 - Apr 2018}
	\resumeItemListStart
	\resumeItem{}
	{Implemented Transparency Feeds using \textbf{RabbitMQ} message broker and \textbf{FIX}(Financial Messaging Protocol) to comply with MiFID 2 regulations}
	\resumeItem{}
	{Applied database partitioning to improve performance on \textbf{Postgresql} database.}
	\resumeItem{}
	{Enforced code review culture to the company and introduced \textbf{Gerrit}.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Monitise MEA (aka Commencis )}{Istanbul (comp. based in London)}
	{Android Engineer}{Nov 2016 - Jul 2017}
	\resumeItemListStart
	\resumeItem{IsCep: }
	{IsCep is the mobile application of Is Bankasi with \textbf{5.2 million active users}. Project uses \textbf{MVC} pattern and cutting edge libraries like \textbf{Retrofit, Eventbus, Mockito} etc.}
	\resumeItem{Owl: }
	{Won internal hackathon by building an Instagram stalker app in 24 hours with a team of three people. App is used to view someone else's "home screen" on Instagram to get a feel of their taste of social media.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Pfizer}{Istanbul (comp. based in NY)}
	{Business Analytics\&Insights Specialist}{Jan 2016 - Nov 2016}
	\resumeItemListStart
	\resumeItem{}
	{Worked as a business partner and a proactive consultant to support, challenge and drive business decisions by providing analyses to lead/support high quality decisions, participating and pro-actively contributing to business initiatives}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Bogazici University}{Istanbul}
	{Bachelor of Engineering in Computer Engineering}{Sep. 2011 -- Jan. 2016}
	\resumeSubheading
	{Bahcesehir High School for Science and Technology}{Istanbul}
	{80th place in 800.000 students in National Selection Exam}{Sep. 2006 -- Jun. 2011}
	\resumeSubHeadingListEnd
	
	
	
	%-----------ACTIVITIES-----------------
	\section{Activities}
	\resumeSubHeadingListStart
	\resumeSubItem{\href{https://skillsmatter.com/conferences/10488-scala-exchange-2018}{Scala Exchange: }}
	{I worked as part of the volunteer organization team in the ScalaX 2018 event in London.}
	\resumeSubItem{Scuba Diving: }
	{CMAS certified 2 star diver. BUSAS (Bogazici University Underwater Sports) certified free diver.}
	\resumeSubItem{Yoga: }
	{Practicing yoga, mindfulness and meditation for 2 years.}
	\resumeSubItem{Running: }
	{Actively running with Adidas Runners Istanbul. Ran Istanbul Half Marathon.}
	\resumeSubItem{Spinning: }
	{Indoor spinning assistant at Urban Riders.}
	\resumeSubHeadingListEnd
	
	
	%-------------------------------------------
\end{document}